---
title: "analysis of non planar Wilson loops, klft output."
output:
  html_document: def
---
Loading parameters and libraries.

```{r}
# load libraries
library(hadron)

boot.l = 500
boot.R = 500
therm = 500

temporal_extent <- 32
spatial_extent <- 3
inv_coupling <- 50

if(spatial_extent == 3)
  r_i <- c(1, sqrt(2), 2, sqrt(5), sqrt(8))
if(spatial_extent == 4)
  r_i <- c(1, sqrt(2), 2, sqrt(5), sqrt(8), sqrt(10), sqrt(18))
if(spatial_extent == 5)
  r_i <- c(1, sqrt(2), 2, sqrt(5), sqrt(8), sqrt(10), sqrt(18), 5, sqrt(32))

extra = "_0"

folder <- paste0("pascal_OBC_", inv_coupling, "_", spatial_extent, "_", temporal_extent, extra)

rawdata <- "/home/negro/projects/matching/RU1/01_rawdata/OBC/"
plots <- "/home/negro/projects/matching/RU1/02_output/plots/OBC/"
datas <- "/home/negro/projects/matching/RU1/02_output/data/OBC/"

dir.create(paste0(plots, folder))
dir.create(paste0(datas, folder))
```

Extracting data into matrix

```{r}
data <- as.matrix(read.table(paste0(rawdata, folder, "/", folder, ".dat"), skip = 1))
```

MCMC history

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
pdf(paste0(plots, folder, "/thermalization.pdf"))
for(i in seq_along(r_i)){
  W <- data[, seq(4 + i, ncol(data), length(r_i))]
  time_series <- W[, 1]
  plot(x = c(1:length(time_series)), y = time_series, xlab = "n_configs", ylab = "W(R,T)", main = paste0("W(R,T) for T = 1, R = ", r_i[i]))

  plot(computeacf(time_series), main = paste0("Autocorrelation function W(R,T) for T = 1, R = ", r_i[i]))
  #summary(myacf)
  #cat("\n")
  rm(W)
  rm(time_series)
}
dev.off()
rm(data)
```
Bootstrap analysis

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
data <- as.matrix(read.table(paste0(rawdata, folder, "/", folder, ".dat"), skip = 1 + therm))

pdf(paste0(plots, folder, "/bootstrap_analysis.pdf"))
for(i in seq_along(r_i)){
  tmp <- data[, seq(5 + (i-1) , ncol(data), length(r_i))]
  Time <- ncol(tmp)
  
  tmp <- cf_orig(cf = tmp)
  tmp <- cf_meta(tmp, nrObs = 1, Time = Time)
  
  bootstrap.analysis(tmp$cf[, 1], boot.R = boot.R, boot.l = 2, pl = TRUE)
  rm(tmp)
}
dev.off()
```

Bootstrapping data

```{r}
W <- list()

for(i in seq_along(r_i)){
  tmp <- data[, seq(5 + (i-1), ncol(data), length(r_i))]
  Time <- ncol(tmp)

  tmp <- cf_orig(cf = tmp)
  tmp <- cf_meta(tmp, nrObs = 1, nrStypes = 0, Time = Time)
  
  W[[length(W) + 1]] <- bootstrap.cf(cf = tmp, boot.R = boot.R, boot.l = boot.l, sim = "fixed", endcorr = TRUE, seed = 1234567)
}

saveRDS(W, paste0(datas, folder, "/Wloops.rds"))
```

Plotting data

```{r}
pdf(paste0(plots, folder, "/NPWL.pdf"))
for(i in seq_along(r_i)){
  plot(W[[i]], main = paste0("Non planar Wilson loop for R = ", r_i[i]), ylab = "W(R,T)", xlab = "t")
  grid()
  plot(W[[i]], log = "y", main = paste0("Non planar Wilson loop for R = ", r_i[i], ", logscale"), ylab = "W(R,T)", xlab = "t")
  grid()
}
```

Effective mass

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
pdf(paste0(plots, folder, "/EMASS.pdf"))
lims <- rep(list(c(0,0.1)), length(r_i))
lims <- list(c(0.015, 0.017), c(0.0145, 0.018), c(0.0199, 0.021), c(0.019, 0.021), c(0.0225, 0.03))
for(i in seq_along(r_i)){
  e_mass <- bootstrap.effectivemass(W[[i]], type = "log")
  plot(e_mass, main = paste0("Effectiva mass for r = ", r_i[i]), ylab = expression(m[eff]), xlab = "t", xlim = c(0,24), ylim = lims[[i]])
  grid()
}
dev.off()
```
Fit stuff

```{r}
if(!exists("W")){
W <- readRDS(paste0(datas, folder, "/Wloops.rds"))
}
range <- seq(1,temporal_extent-1)
mask <- list(seq(6, 16), seq(6, 16), seq(6, 16), seq(6, 16), seq(6, 16))

fn <- function(par, x, boot.r, ...) par[1] * exp(-par[2] * x)
```

Fit routine uncorrelated data

```{r}
pdf(paste0(plots, folder, "/uncorrelated_fit.pdf"))

for(i in seq_along(r_i)){
  value <- W[[i]]$cf.tsboot$t0
  bsamples <- W[[i]]$cf.tsboot$t

  fit.result_uncorrelated <- bootstrap.nlsfit(fn = fn, par.guess = c(0.05, 0.02), y = value, x = range, bsamples = bsamples, mask = mask[[i]], use.minpack.lm = FALSE)

  plot(fit.result_uncorrelated, main = paste0("Fit with a*exp(-E_0*t) with r = ", r_i[i]), ylab = "W(R,T)", xlab = "t", xlim = c(mask[[i]][1], mask[[i]][length(mask[[i]])]), ylim =rev(c(value[mask[[i]][1]], value[mask[[i]][length(mask[[i]])]])), log = "y")
  legend(x = "topright", legend = c(paste0("chi2 = ", round(fit.result_uncorrelated$chisqr,2)), paste0("dof = ", fit.result_uncorrelated$dof), paste0("a = ", round(fit.result_uncorrelated$t0[1], 5)), paste0("da = ", round(fit.result_uncorrelated$se[1], 5)), paste0("E_0 = ", round(fit.result_uncorrelated$t0[2], 5)), paste0("dE_0 = ", round(fit.result_uncorrelated$se[2], 5))))
  
    plot(fit.result_uncorrelated, main = paste0("Fit with a*exp(-E_0*t) with r = ", r_i[i]), ylab = "W(R,T)", xlab = "t", log = "y")
  legend(x = "topright", legend = c(paste0("chi2 = ", round(fit.result_uncorrelated$chisqr,2)), paste0("dof = ", fit.result_uncorrelated$dof), paste0("a = ", round(fit.result_uncorrelated$t0[1], 5)), paste0("da = ", round(fit.result_uncorrelated$se[1],5)), paste0("E_0 = ", round(fit.result_uncorrelated$t0[2], 5)), paste0("dE_0 = ", round(fit.result_uncorrelated$se[2], 5))))
  
  dof <- fit.result_uncorrelated$dof
  chi2 <- fit.result_uncorrelated$chisqr
  
  print(paste0("R = ", r_i[i]))
  print("result")
  print(fit.result_uncorrelated$t0)
  print("error")
  print(fit.result_uncorrelated$se)
  print("chi2/dof")
  print(chi2/dof)
  cat("\n")
  
  saveRDS(fit.result_uncorrelated, paste0(datas, folder, "/fit.result_uncorrelated_", i,".rds"))
}
dev.off()
```
Fit routine correlated

```{r}
pdf(paste0(plots, folder, "/correlated_fit.pdf"))
for(i in seq_along(r_i)){
  value <- W[[i]]$cf.tsboot$t0
  bsamples <- W[[i]]$cf.tsboot$t
  
  fit.result_correlated <- bootstrap.nlsfit(fn = fn, par.guess = c(0.05, 0.02), y = value, x = range, bsamples = bsamples, mask = mask[[i]], use.minpack.lm = FALSE, CovMatrix = NULL)
  
    plot(fit.result_correlated, main = paste0("Fit with a*exp(-E_0*t) with r = ", r_i[i]), ylab = "W(R,T)", xlab = "t", xlim = c(0,32), log = "y")
  legend(x = "topright", legend = c(paste0("chi2 = ", round(fit.result_correlated$chisqr,2)), paste0("dof = ", fit.result_correlated$dof), paste0("a = ", round(fit.result_correlated$t0[1], 5)), paste0("da = ", round(fit.result_correlated$se[1],5)), paste0("E_0 = ", round(fit.result_correlated$t0[2], 5)), paste0("dE_0 = ", round(fit.result_correlated$se[2], 5))))
  
  dof <- fit.result_correlated$dof
  chi2 <- fit.result_correlated$chisqr
  
  print(paste0("R = ", r_i[i]))
  print("result")
  print(fit.result_correlated$t0)
  print("error")
  print(fit.result_correlated$se)
  print("chi2/dof")
  print(chi2/dof)
  cat("\n")
  
  saveRDS(fit.result_correlated, paste0(datas, folder, "/fit.result_correlated_", i,".rds"))
}
dev.off()
```
computing r2F

```{r echo = FALSE}
g1Lst <- list()
g2Lst <- list()

VLst <- list()

temporal_extent <- 32
inv_coupling <- 1.4
spatial_extent_array <- c(3, 4, 5)
boot.R = 500
r_i <- c(1, sqrt(2), 2, sqrt(5), sqrt(8), sqrt(10), sqrt(18), 5, sqrt(32))
extra = "_0"

rawdata <- "/home/negro/projects/matching/RU1/01_rawdata/OBC/"
plots <- "/home/negro/projects/matching/RU1/02_output/plots/"
datas <- "/home/negro/projects/matching/RU1/02_output/data/"
plots_SS <- "/home/negro/projects/matching/RU1/02_output/plots/stepScalingPlots/"

for (i in seq_along(spatial_extent_array)){
  folder <- paste0("pascal_OBC_", inv_coupling, "_", spatial_extent_array[i], "_", temporal_extent, extra)

  V <- rep(NA, length(r_i))
  bsV_3 <- matrix(NA, nrow = boot.R, ncol = length(r_i))
  dV <- rep(NA, length(r_i))
  
  for(j in seq_along(r_i)){
    tmp <- readRDS(paste0(datas, folder, "/fit.result_correlated_", j,".rds"))
    V[j] <- tmp$t0[[2]]
    bsV[,j] <- tmp$t[,2]
    dV[j] <- tmp$se[[2]]
  }
  
  g1 <- r_i[1]*r_i[1]*(V[2]-V[1])/(r_i[2]-r_i[1])
  g2 <- r_i[2]*r_i[2]*(V[3]-V[2])/(r_i[3]-r_i[2])
  
  bsg1 <- r_i[1]*r_i[1]*(bsV[,2]-bsV[,1])/(r_i[2] - r_i[1])
  bsg2 <- r_i[2]*r_i[2]*(bsV[,3]-bsV[,2])/(r_i[3] - r_i[2])
  
  sublist <- list(V, bsV, dV)
  VLst[[i]] <- sublist
  
  sublist <- list(g1, bsg1)
  g1Lst[[i]] <- sublist 
  
  sublist <- list(g2, bsg2)
  g2Lst[[i]] <- sublist
}
rm(sublist)
rm(tmp)

dir.create(paste0(plots, "/stepScalingPlots/E0_r2F_b", inv_coupling,"_OBC", extra))
```

Here is a plot of the ground state energy for r = 1

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))
bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))
dvalue <- rep(NA, length(x))

for(i in seq_along(x)){
  value[i] <- VLst[[i]][[1]][1]
  bsamples[,i] <- VLst[[i]][[2]][,1]
  dvalue[i] <- VLst[[i]][[3]][1]
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/E0_1.pdf"))
plotwitherror(x, value, dvalue, main = paste0("E_0 for r = ", r_i[1], " beta = ", inv_coupling), xlab = "L/a", ylab = "E_0")
dev.off()
print(apply(bsamples, 2, sd))
print(dvalue)
```

Here is a plot of the ground state energy for r = sqrt(2)

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))
bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))
dvalue <- rep(NA, length(x))

for(i in seq_along(x)){
  value[i] <- VLst[[i]][[1]][2]
  bsamples[,i] <- VLst[[i]][[2]][,2]
  dvalue[i] <- VLst[[i]][[3]][2]
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/E0_sqrt2.pdf"))
plotwitherror(x, value, dvalue, main = paste0("E_0 for r = ", r_i[2], " beta = ", inv_coupling), xlab = "L/a", ylab = "E_0")
dev.off()
```

Plot of the ground state energy for r = 2

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))
bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))
dvalue <- rep(NA, length(x))

for(i in seq_along(x)){
  value[i] <- VLst[[i]][[1]][3]
  bsamples[,i] <- VLst[[i]][[2]][,3]
  dvalue[i] <- VLst[[i]][[3]][3]
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/E0_2.pdf"))
plotwitherror(x, value, dvalue, main = paste0("E_0 for r = ", r_i[3], " beta = ", inv_coupling), xlab = "L/a", ylab = "E_0")
dev.off()
```
Plot of the ground state energy for r = sqrt(5)

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))
bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))
dvalue <- rep(NA, length(x))

for(i in seq_along(x)){
  value[i] <- VLst[[i]][[1]][4]
  bsamples[,i] <- VLst[[i]][[2]][,4]
  dvalue[i] <- VLst[[i]][[3]][4]
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/E0_sqrt5.pdf"))
plotwitherror(x, value, dvalue, main = paste0("E_0 for r = ", r_i[4], " beta = ", inv_coupling), xlab = "L/a", ylab = "E_0")
dev.off()
```

Here is a plot of the running coupling r^2F(r,g) for r = 1

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))
bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))

for(i in seq_along(x)){
  value[i] <- as.numeric(g1Lst[[i]][1])
  bsamples[,i] <- unlist(g1Lst[[i]][2])
}

value <- unlist(value)
bsamples <- as.matrix(bsamples, nrow = boot.R, ncol = length(x))

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/r2F_1.pdf"))
plotwitherror(x, value, apply(bsamples, 2, sd), main = paste0("g(r,beta) for r = ", r_i[1], " beta = ", inv_coupling), xlab = "L/a", ylab = "g(r1,beta)")
dev.off()
```

Here is a plot of the running coupling r^2F(r,g) for r = sqrt2

```{r echo = FALSE}
x <- spatial_extent_array

value <- rep(NA, length(x))

bsamples <- matrix(NA, nrow = boot.R, ncol = length(x))

for(i in seq_along(x)){
  value[i] <- as.numeric(g2Lst[[i]][1])
  bsamples[,i] <- unlist(g2Lst[[i]][2])
}

value <- unlist(value)
bsamples <- as.matrix(bsamples, nrow = boot.R, ncol = length(x))

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/r2F_sqrt2.pdf"))
plotwitherror(x, value, apply(bsamples, 2, sd), main = paste0("g(r,beta) for r = ", r_i[2], " beta = ", inv_coupling), xlab = "L/a", ylab = "g(r2,beta)")
dev.off()
```

plot for E0(r) at fixed L

```{r}
x <- c(3, 4, 5)

value1 <- rep(NA, length(x))
value2 <- rep(NA, length(x))
value3 <- rep(NA, length(x))

bsamples1 <- matrix(NA, nrow = boot.R, ncol = length(x))
bsamples2 <- matrix(NA, nrow = boot.R, ncol = length(x))
bsamples3 <- matrix(NA, nrow = boot.R, ncol = length(x))

for(i in seq_along(x)){
  value1[i] <- VLst[[i]][[1]][1]
  bsamples1[,i] <- VLst[[i]][[2]][,1]
  value2[i] <- VLst[[i]][[1]][2]
  bsamples2[,i] <- VLst[[i]][[2]][,2]
  value3[i] <- VLst[[i]][[1]][3]
  bsamples3[,i] <- VLst[[i]][[2]][,3]
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/E0_vs_r.pdf"))
  plotwitherror(x, value1, apply(bsamples1, 2, sd), col = "red", ylim = c(0.45, 0.95), ylab = "E_0", xlab = "L/a", main = "E_0(L) for different distances r", cex = 1.2)
  plotwitherror(x, value2, apply(bsamples2, 2, sd), col = "blue", rep = TRUE,  cex = 1.2)
  plotwitherror(x, value3, apply(bsamples3, 2, sd), col = "green", rep = TRUE,  cex = 1.2)
  legend(x = "topright", legend = c("r=1", "r=sqrt(2)", "r=sqrt(5)"), pch = 1, cex = 1.2, col = c("red", "blue", "green"))
dev.off()
```

Plotting r2F vs r at fixed L

```{r}
x <- c(3, 4, 5)

value1 <- rep(NA, length(x))
value2 <- rep(NA, length(x))

bsamples1 <- matrix(NA, nrow = boot.R, ncol = length(x))
bsamples2 <- matrix(NA, nrow = boot.R, ncol = length(x))

for(i in seq_along(x)){
  value1[i] <- as.numeric(g1Lst[[i]][1])
  bsamples1[,i] <- unlist(g1Lst[[i]][2])
  value2[i] <- as.numeric(g2Lst[[i]][1])
  bsamples2[,i] <- unlist(g2Lst[[i]][2])
}

pdf(paste0(plots_SS, "E0_r2F_b", inv_coupling,"_OBC", extra,"/r2F_vs_r.pdf"))
  plotwitherror(x, value1, apply(bsamples1, 2, sd), col = "red", ylim = c(0.35, 0.8), main = "g=r^2*dV/dr(L) for different values of r", xlab = "L/a", ylab = "g")
  plotwitherror(x, value2, apply(bsamples2, 2, sd), col = "blue", rep = TRUE)
  legend(x = "topright", legend = c("r=1", "r=sqrt(2)"), pch = 1, cex = 1.2, col = c("red", "blue"))
dev.off()
```
Step Scaling for L = 3

```{r}
temporal_extent <- 32
spatial_extent <- 3
boot.R = 500
r_i <- c(1, sqrt(2), sqrt(5))
extra = "_0"

rawdata <- "/home/negro/projects/matching/RU1/01_rawdata/OBC/"
plots <- "/home/negro/projects/matching/RU1/02_output/plots/"
datas <- "/home/negro/projects/matching/RU1/02_output/data/"
plots_SS <- "/home/negro/projects/matching/RU1/02_output/plots/stepScalingPlots/"

# L = 3
inv_coupling_array <- c(1.4, 1.7, 2.0, 3.0)

g1_lst <- list()
g2_lst <- list()

bsg1_lst <- list()
bsg2_lst <- list()

V <- rep(NA, length(inv_coupling_array))
bsV <- matrix(NA, nrow = boot.R, ncol = length(inv_coupling_array))

for(i in inv_coupling_array)
{
  folder <- paste0("pascal_OBC_", i, "_", 3, "_", temporal_extent, extra)
    
  for(j in seq_along(r_i))
  {
    tmp <- readRDS(paste0(datas, folder, "/fit.result_correlated_", j,".rds"))
    V[j] <- tmp$t0[[2]]
    bsV[,j] <- tmp$t[,2]
  }
  
  g1 <- r_i[1]*r_i[1]*(V[2]-V[1])/(r_i[2]-r_i[1])
  g2 <- r_i[2]*r_i[2]*(V[3]-V[2])/(r_i[3]-r_i[2])
  
  bsg1 <- r_i[1]*r_i[1]*(bsV[,2]-bsV[,1])/(r_i[2] - r_i[1])
  bsg2 <- r_i[2]*r_i[2]*(bsV[,3]-bsV[,2])/(r_i[3] - r_i[2])

  g1_lst[[length(g1_lst) + 1]] <- g1
  bsg1_lst[[length(bsg1_lst) + 1]] <- bsg1
  
  g2_lst[[length(g2_lst) + 1]] <- g2
  bsg2_lst[[length(bsg2_lst) + 1]] <- bsg2 
}
rm(g1)
rm(g2)
rm(bsg1)
rm(bsg2)

g1 <- as.numeric(g1_lst)
g2 <- as.numeric(g2_lst)

bsg1 <- matrix(unlist(bsg1_lst), nrow = boot.R, ncol = length(inv_coupling_array))
bsg2 <- matrix(unlist(bsg2_lst), nrow = boot.R, ncol = length(inv_coupling_array))

rm(bsg1_lst)
rm(bsg2_lst)
rm(g1_lst)
rm(g2_lst)

x <- inv_coupling_array

y1 <- g1
dy1 <- apply(bsg1, 2, sd)

y2 <- g2
dy2 <- apply(bsg2, 2, sd)

pdf(paste0(plots_SS, "test.pdf"))
  plotwitherror(x, y1, dy1, col = "blue", pch = 2, cex = 1.5, ylim = c(0, 0.8), xlab = "beta=1/g²", ylab = "r²F(r,g)")
  grid()
  plotwitherror(x, y2, dy2, col = "blue", pch = 6, cex = 1.5, rep = TRUE)
  
  # L = 4
inv_coupling_array <- c(1.4, 1.7, 2.0, 3.0)

g1_lst <- list()
g2_lst <- list()

bsg1_lst <- list()
bsg2_lst <- list()

V <- rep(NA, length(inv_coupling_array))
bsV <- matrix(NA, nrow = boot.R, ncol = length(inv_coupling_array))

for(i in inv_coupling_array)
{
  folder <- paste0("pascal_OBC_", i, "_", 4, "_", temporal_extent, extra)
    
  for(j in seq_along(r_i))
  {
    tmp <- readRDS(paste0(datas, folder, "/fit.result_correlated_", j,".rds"))
    V[j] <- tmp$t0[[2]]
    bsV[,j] <- tmp$t[,2]
  }
  
  g1 <- r_i[1]*r_i[1]*(V[2]-V[1])/(r_i[2]-r_i[1])
  g2 <- r_i[2]*r_i[2]*(V[3]-V[2])/(r_i[3]-r_i[2])
  
  bsg1 <- r_i[1]*r_i[1]*(bsV[,2]-bsV[,1])/(r_i[2] - r_i[1])
  bsg2 <- r_i[2]*r_i[2]*(bsV[,3]-bsV[,2])/(r_i[3] - r_i[2])

  g1_lst[[length(g1_lst) + 1]] <- g1
  bsg1_lst[[length(bsg1_lst) + 1]] <- bsg1
  
  g2_lst[[length(g2_lst) + 1]] <- g2
  bsg2_lst[[length(bsg2_lst) + 1]] <- bsg2 
}
rm(g1)
rm(g2)
rm(bsg1)
rm(bsg2)

g1 <- as.numeric(g1_lst)
g2 <- as.numeric(g2_lst)

bsg1 <- matrix(unlist(bsg1_lst), nrow = boot.R, ncol = length(inv_coupling_array))
bsg2 <- matrix(unlist(bsg2_lst), nrow = boot.R, ncol = length(inv_coupling_array))

rm(bsg1_lst)
rm(bsg2_lst)
rm(g1_lst)
rm(g2_lst)

x <- inv_coupling_array

y1 <- g1
dy1 <- apply(bsg1, 2, sd)

y2 <- g2
dy2 <- apply(bsg2, 2, sd)

plotwitherror(x, y1, dy1, col = "red", pch = 1, cex = 1.5, rep = TRUE)
plotwitherror(x, y2, dy2, col = "red", pch = 1, cex = 1, rep = TRUE)

par(xpd=TRUE, mar=c(5, 4, 6, 2))

legend(x = "top", inset = c(0, -0.15),
       legend = c(expression(r[1]^2 ~ F(r[1], g) ~ "3x3"), 
             expression(r[2]^2 ~ F(r[2], g) ~ "3x3"), 
             expression(r[1]^2 ~ F(r[1], g) ~ "4x4"), 
             expression(r[2]^2 ~ F(r[2], g) ~ "4x4")),, pch = c(2, 6, 1, 1), pt.cex = c(1.5, 1.5, 1.5, 1), col = c("blue", "blue", "red", "red"), y.intersp = 1.5, ncol = 2, bty = "n")


dev.off()



```

